### 2021-03-31 README.Rmd
update readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio)

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "World Heritage Sites on Wikipedia: Cultural Heritage Activism in a Context of Constrained Agency"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio) [![Knit-Rmd-in-Docker](https://github.com/benmarwick/worldheritagewikipedia/workflows/.github/workflows/knit-Rmd-in-docker.yaml/badge.svg)](https://github.com/benmarwick/worldheritagewikipedia/actions)

@@

> Marwick, B and P. Smith, (2021). `r Title`. _Big Data and Society_ <https://doi.org/xxx/xxx>

@@

> Marwick, B and P. Smith, (2021). `r Title`.  Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31235/osf.io/7gvza>

@@

> Marwick, B and P. Smith, (`r format(Sys.Date(), "%Y")`). Compendium of R code and data for `r Title`. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/AY27G>

## Contents

The **analysis** directory contains:

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript and R script files. Includes R code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations using in the paper
